### 2015-02-22 fundamentals/impl.tex
updated cyclopts mention

Cyclopts \cite{gidden_cyclopts_2015}, a proof of principle design and
implementation of \Cyclus on such a large computer system, uses UW-Madison's
HTCondor \gls{HTC} infrastructure to perform sensitivity studies on \Cyclus'
resource exchange optimization solvers. To date, it has been used to run over
$10^4$ jobs, or (\TODO{compute time}) total compute hours, using the \Cyclus
library via its resource exchange \gls{API}.  The \gls{HTC} infrastructure has
also been utilized to run and collect information from full \Cyclus simulations
running in parallel on $10^3$ machines reliably for order $10^5$ simulations.

>>>>

Cyclopts \cite{gidden_cyclopts_2015}, a proof of principle design and
implementation of a \Cyclus-enabled application on such a large computer system,
uses UW-Madison's HTCondor \gls{HTC} infrastructure to perform sensitivity
studies on \Cyclus' resource exchange optimization solvers. To date, it has been
used to run over $10^5$ jobs, comprising more than 60,000 total compute hours,
using the \Cyclus library via its resource exchange \gls{API}.  The \gls{HTC}
infrastructure has separately been utilized to run and collect information from
full \Cyclus simulations running in parallel on $10^3$ machines reliably for
order $10^5$ simulations.
